SMT-Based Context-Bounded Model Checking for Embedded Systems (Position Paper)

### 2016-03-18 paper.tex
review achievements

The \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,GrosseLD09,Sheera00}. However, there is still little evidence, in the available literature, that model checking hardware and software systems, using \textit{k}-induction (and invariants), can be efficiently exploited in embedded system verification~\cite{Rocha15,Brain15,Brain15}. That happens due to the distinctive characteristics mentioned earlier, which influence the embedded system development and also the employed verification processes.

@@

\textbf{(RP1)} Cordeiro {\it et al.} proposed the first SMT-based BMC for full C programs, called Efficient SMT-Based Context-Bounded Model Checker (ESBMC)~\cite{Cordeiro12}, which was later extended to support C++98 programs~\cite{ECBS13} and Qt programs~\cite{Sousa15}.

\textbf{(RP2)} This SMT-based BMC approach was further developed to verify deadlock, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering partial-order reduction and state-hashing techniques, in order to prune the state-space exploration~\cite{morse15}. Such verification methodologies and respective tools were also able to find undiscovered bugs related to arithmetic overflow, buffer overflow, and invalid pointer, in standard benchmarks, which were later confirmed by the benchmarks' creators ({\it e.g.}, NOKIA, NEC, NXP, and VERISEC).

\textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated, which demonstrates is effectiveness in some real-life embedded system applications~\cite{Gadelha15,Rocha15}.

@@

\bibitem{pips:2013}
ParisTech M (2013) PIPS: Automatic Parallelizer and Code Transformation Framework. Accessed 21 February 2016

\bibitem{Henry:2012}
 Henry J, Monniaux D, Moy M (2012) PAGAI: A Path Sensitive Static Analyser. Electronic Notes in Theoretical Computer Science. Elsevier, pp. 15--25

@@

>>>>

The \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,GrosseLD09,Sheera00}. However, there is still little evidence, in the available literature, that model checking hardware and software systems, using \textit{k}-induction (and invariants), can be efficiently exploited in embedded system verification~\cite{Rocha15,Beyer15,Brain15}. That happens due to the distinctive characteristics mentioned earlier, which influence the embedded system development and also the employed verification processes.

@@

\textbf{(RP1)} Cordeiro {\it et al.} proposed the first SMT-based BMC for full C programs, called Efficient SMT-Based Context-Bounded Model Checker (ESBMC)~\cite{Cordeiro12}, which was later extended to support C++98 programs~\cite{ECBS13} and Qt-based consumer electronics applications~\cite{Sousa15}. Other efficient SMT-based BMC approaches have been proposed and implemented~\cite{MerzFS12}, but the coverage and verification time of all existing approaches are still limited for specific class of programs, especially for those that contain floating-point arithmetic and manipulate the heap memory~\cite{BeyerSVCOMP15}.

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro {\it et al.} was further developed to verify deadlock, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering partial-order reduction and state-hashing techniques, in order to prune the state-space exploration~\cite{morse15}. Such verification methodologies and respective tools were also able to find undiscovered bugs related to arithmetic overflow, buffer overflow, and invalid pointer, in standard benchmarks, which were later confirmed by the benchmarks' creators ({\it e.g.}, NOKIA, NEC, NXP, and VERISEC). Recent advances to verify multi-threaded C programs have been made by Inverso {\it et al.}~\cite{Inverso14}, but the class of programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited.

\textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated, which demonstrates its effectiveness in some real-life embedded system applications~\cite{Gadelha15,Rocha15,Brain15}. However, the main challenge still remains to compute and strengthen loop invariants to prove program correctness. Invariant generation algorithms must still evolve to efficiently discover inductive assertions of programs or to continuously refine invariants, as described by Beyer {\it et al.}~\cite{Beyer15}.

@@

\bibitem{pips:2013}
ParisTech M.:
\newblock {\em PIPS: Automatic Parallelizer and Code Transformation Framework.} 
\newblock Accessed 21 February 2016

\bibitem{Henry:2012}
Henry J., Monniaux D., Moy M.: 
\newblock {\em PAGAI: A Path Sensitive Static Analyser.} 
\newblock In: Electronic Notes in Theoretical Computer Science, pp. 15--25, 2012.

\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

@@

\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}
\newblock In: Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.
